---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# clustersims

<!-- badges: start -->
<!-- badges: end -->

The goal of `clustersims` is to compare rejection rates of different methods for cluster robust inference. The data generating process follows MacKinnon, Nielsen & Webb's "Fast and Reliable" paper (2023).

## Installation

You can install the development version of clustersims from github by typing

```{r, eval = FALSE}
library(devtools)
install_github("s3alfisc/clustersims")
```


## Example

```{r, eval = FALSE}
set.seed(8795)

# note that this will run for a very long time
pracma::tic()

library(clustersims)
run_clustersim(
  n_sims = 100000, 
  workers = 8,
  filename = "cluster_simulation2"
)
pracma::toc()
```

## Other Simulations

- Romano Wolf corrections: [wildrwolf](https://github.com/s3alfisc/wildrwolf#but-does-it-work-monte-carlo-experiments)
- [other dgp's](https://github.com/s3alfisc/clusteredErrorsSims)
